Project Proposal

### 2025-01-08 proposal_EDA/deGuzman_IDS702Projectproposal_template.qmd

# Plot with short-term race labels on the x-axis and percentage labels on the bars
ggplot(data, aes(x = Race_Ethnicity, fill = Q1R5_cleaned)) +
  geom_bar(position = "fill") +
  labs(title = "Importance of Stopping Discrimination by Race/Ethnicity",
       x = "Race/Ethnicity",
       y = "Proportion",
       fill = "Importance Level",
       caption = "Race/Ethnicity Abbreviations: ANAI = Native American, NH = Native Hawaiian, AAPI = Asian American/Pacific Islander, MENA = Middle Eastern/North African") +
  scale_y_continuous(labels = scales::percent) +
  theme_minimal() +
  geom_text(aes(label = scales::percent(after_stat(count)/sum(after_stat(count)))),
            stat = "count", 
            position = position_fill(vjust = 0.5),
            color = "white")
```

>>>>

# Plot with short-term race labels on the x-axis and percentage labels on the bars
ggplot(data, aes(x = Race_Ethnicity, fill = Q1R5_cleaned)) +
  geom_bar(position = "fill") +
  labs(title = "Importance of Stopping Discrimination by Race/Ethnicity",
       x = "Race/Ethnicity",
       y = "Proportion",
       fill = "Importance Level",
       caption = "Race/Ethnicity Abbreviations: ANAI = Native American, NH = Native Hawaiian, AAPI = Asian American/Pacific Islander, MENA = Middle Eastern/North African") +
  scale_y_continuous(labels = scales::percent) +
  theme_minimal() 
```
